---
title: "INFO 241"
author: "CS"
date: "2022-11-09"
output: html_document
---

```{r setup, echo = FALSE}

library(sandwich)
library(lmtest)
library(broom)
library(data.table)
library(tidyverse)
library(stargazer)

# set theme for ggplot
theme_set(theme_minimal())

# set up color scheme
m_nt <- "#C97137"
m_t <- "#E0B190"
w_nt <- "#3F6BA5"
w_t <- "#97B3D8"
color_scheme <- c(m_nt, m_t, w_nt, w_t)

```


```{r load and clean data, echo = FALSE}

df <- read.csv("info241_raw.csv")
df <- cbind(pt = 1:nrow(df), df)

# update the scale column names
cols_old <- colnames(df)
cols_new <- str_replace_all(cols_old, 
                            c(
                              "m_nt" = "man_nontrad",
                              "m_t" = "man_trad", 
                              "w_nt" = "woman_nontrad",
                              "w_t" = "woman_trad",
                              "scale_12" = "scale_education",
                              "scale_13" = "scale_experience",
                              "scale_1" = "scale_technical",
                              "scale_3" = "scale_leadership",
                              "scale_4" = "scale_likeable",
                              "scale_5" = "scale_learner")
)
colnames(df) <- cols_new

df$risk <- rowMeans(df %>% select(contains("risk")))


# make list of columns for participant information
participant_columns <- c('pt', 'age', 'gender', 'gender_5_TEXT', 'employment', 'role', 'company_size', 'experience', 'roles', 'industry', 'industry_12_TEXT', "risk", "Condition")
participant_columns_remove <- c('gender_5_TEXT', 'employment', 'role', 'experience', 'roles', 'industry', 'industry_12_TEXT')

# make participant information df
pt_info <- select(df, all_of(participant_columns))

# make analysis df
analysis <- df %>%
  select(matches(c("man")))
analysis <- cbind(pt = df$pt, analysis)

# use gather to make long data from wide data
analysis <- gather(df, source, rating, colnames(analysis %>% select(matches("man")) %>% select(-contains("scale"))))

# split out the source columns
analysis[c("applicant_gender", "applicant_education", "stimuli_number")] <- str_split_fixed(analysis$source, '_', 3)

# remove rows with NA values
analysis <- analysis %>% drop_na(rating) %>% 
  select(-contains("aversion")) %>% 
  select(-all_of(participant_columns_remove))

# condense across scale ratings
# create lists of columns to condense
technical_scale_cols <- colnames(analysis %>% select(matches("scale_technical")))
leadership_scale_cols <- colnames(analysis %>% select(matches("scale_leadership")))
likeable_scale_cols <- colnames(analysis %>% select(matches("scale_likeable")))
learner_scale_cols <- colnames(analysis %>% select(matches("scale_learner")))
education_scale_cols <- colnames(analysis %>% select(matches("scale_education")))
experience_scale_cols <- colnames(analysis %>% select(matches("scale_experience")))
# condense and remove columns
analysis <- analysis %>%
  mutate(technical_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[technical_scale_cols], sep = ",")), "NA,"), ",NA"),
         leadership_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[leadership_scale_cols], sep = ",")), "NA,"), ",NA"),
         likeable_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[likeable_scale_cols], sep = ",")), "NA,"), ",NA"),
         learner_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[learner_scale_cols], sep = ",")), "NA,"), ",NA"),
         education_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[education_scale_cols], sep = ",")), "NA,"), ",NA"),
         experience_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[experience_scale_cols], sep = ",")), "NA,"), ",NA")) %>% 
  select(technical_scale, leadership_scale, likeable_scale, learner_scale, education_scale, experience_scale, 
         colnames(analysis)[! colnames(analysis) %in% c(technical_scale_cols, leadership_scale_cols,
                                                        likeable_scale_cols, learner_scale_cols, education_scale_cols,
                                                        experience_scale_cols, "stimuli_number", "source", "Iteration")])

# move into separate rows and remove duplicates
analysis <- analysis %>% 
  mutate(technical_scale = strsplit(technical_scale, ","),
         leadership_scale = strsplit(leadership_scale, ","),
         likeable_scale = strsplit(likeable_scale, ","),
         learner_scale = strsplit(learner_scale, ","),
         education_scale = strsplit(education_scale, ","),
         experience_scale = strsplit(experience_scale, ",")
  ) %>% 
  unnest(c(technical_scale,
           leadership_scale,
           likeable_scale,
           learner_scale,
           education_scale,
           experience_scale)
  )%>% 
  distinct()

# make scales numeric
analysis <- analysis %>% 
  mutate(technical_scale = as.numeric(unlist(technical_scale)),
         leadership_scale = as.numeric(unlist(leadership_scale)),
         likeable_scale = as.numeric(unlist(likeable_scale)),
         learner_scale = as.numeric(unlist(learner_scale)),
         education_scale = as.numeric(unlist(education_scale)),
         experience_scale = as.numeric(unlist(experience_scale))
  )

# create reference condition for analyses
analysis$Condition <- relevel(factor(analysis$Condition), ref = "Man_Traditional")
analysis$applicant_gender <- relevel(factor(analysis$applicant_gender), ref = "man")
analysis$applicant_education <- relevel(factor(analysis$applicant_education), ref = "trad")

```

## Participant Information 

Here, we examine participant demographics, such as their age and gender, in addition to information about their work industry and experience. Overall, our sample is highly skewed in terms of gender. A representative average participant would be a man who works in a relatively large technology company with some years of experience. 

```{r descriptive_information, echo = FALSE}

lightgray <- "#c5c5c5"
darkgray <- "#555555"

age_dist <- ggplot(pt_info, aes(x = age))+
  geom_histogram(fill = lightgray)+
  geom_vline(aes(xintercept = mean(age)), color = darkgray)+
  labs(title = "Distribution of Participant Age",
       subtitle = paste0("Average age is about ", round(mean(pt_info$age), 0)),
       x = "Age",
       y = "Count")
age_dist

gender_dist <- ggplot(pt_info, aes(x = as.factor(gender)))+
  geom_bar(stat = "count", position= "dodge", fill = lightgray)+
  scale_x_discrete(limits = c("Man", "Woman", "Non-binary / third gender", "Prefer not to say"))+
  labs(title = "Distribution of Participant Gender",
       subtitle = paste0("Sample was about ", 
                         round(nrow(subset(pt_info, gender == "Man"))/nrow(pt_info), 2) * 100,
                         "% Men"),
       x = "Reported Gender",
       y = "Count")
gender_dist

employment_dist <- ggplot(pt_info, aes(x = as.factor(employment)))+
  geom_bar(stat = "count", position= "dodge", fill = lightgray)+
  labs(title = "Distribution of Participant Employment Status", 
       subtitle = paste0(
         round(
           nrow(subset(pt_info, employment == "Employed full time"))/nrow(pt_info), 
           2) * 100,
         "% of respondents were employed full time; this was our aim."),
       x = "Employment Status",
       y = "Count")
employment_dist

industry_df <- pt_info %>% 
  mutate(across('industry', str_replace_all, c('Transportation, utilities, or wholesale' = 'Transportation utilities or wholesale',
                                               "Agriculture, mining, or construction" = "Agriculture mining or construction"))) %>% 
  unnest(industry) %>% 
  mutate(industry = strsplit(industry, ",")) %>%
  unnest(industry )%>% 
  group_by(industry) %>% 
  summarise(ct = n()) %>% 
  arrange(desc(ct)) 
industry_dist <- ggplot(industry_df %>% top_n(10) , aes(x = factor(industry, levels = industry), y  = ct))+
  geom_bar(stat = "identity", fill = lightgray)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Distribution of Participant Industry", 
       subtitle = paste0(
         round(subset(industry_df, industry == "Technology")$ct / nrow(pt_info), 2) * 100,
         "% of participants work in Tehcnology"
       ),
       x = "Industry Area",
       y = "Count")
industry_dist


size_dist <- ggplot(pt_info, aes(x = factor(str_replace_all(company_size, " employees", ""),
                                            levels = c("Less than 50",
                                                       "50-100",
                                                       "100-500",
                                                       "500-1,000",
                                                       "1,000+"))))+
  geom_bar(stat = "count", fill = lightgray)+
  labs(title = "Distribution of Participant Company Size",
       subtitle = "Number of employees",
       x = "Company Size",
       y = "Count")
size_dist

experience_dist <- ggplot(pt_info, aes(x = factor(experience,
                                                  levels = c("Less than 1 year",
                                                             "1-2 years",
                                                             "3-5 years",
                                                             "5-10 years",
                                                             "10+ years"))))+
  geom_bar(stat = "count", fill = lightgray)+
  labs(title = "Distribution of Participant Work Experience",
       subtitle = "",
       x = "Years of Experience",
       y = "Count")
experience_dist

risk_dist <- ggplot(pt_info, aes(x = risk))+
  geom_bar(stat = "count", fill = lightgray)+
  geom_vline(aes(xintercept = mean(risk)), color = darkgray)+
  labs(title = "Distribution of Participant Risk Aversion",
       subtitle = paste0("Average risk score is about ", round(mean(pt_info$risk), 2)),
       x = "Average Response to Risk Items",
       y = "Count")
risk_dist

```

### Covariate checks between conditions

```{r covariate_checks}

ggplot(pt_info, aes(x = age))+
  geom_histogram(bins = 30, aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Age",
       subtitle = "Age was relatively similar across conditions.",
       x = "Age",
       y = "Count")+
  facet_grid(Condition ~ .)+
  theme(strip.text.y = element_text(angle = 0))

pt_info %>% 
  group_by(Condition) %>% 
  summarise(avg_age = mean(age))

ggplot(pt_info, aes(x = as.factor(gender)))+
  geom_bar(stat = "count", position= "dodge", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  scale_x_discrete(limits = c("Man", "Woman", "Non-binary / third gender", "Prefer not to say"))+
  labs(title = "Distribution of Participant Gender and Condition",
       subtitle = "Gender was relatively similar across conditions.",
       x = "Reported Gender",
       y = "Count")

industry_dist <- ggplot(industry_df %>% top_n(10) , aes(x = factor(industry, levels = industry), y  = ct))+
  geom_bar(stat = "identity", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Distribution of Participant Industry", 
       subtitle = paste0(
         round(subset(industry_df, industry == "Technology")$ct / nrow(pt_info), 2) * 100,
         "% of participants work in Tehcnology"
       ),
       x = "Industry Area",
       y = "Count")


ggplot(pt_info, aes(x = factor(str_replace_all(company_size, " employees", ""),
                               levels = c("Less than 50",
                                          "50-100",
                                          "100-500",
                                          "500-1,000",
                                          "1,000+"))))+
  geom_bar(stat = "count", position = "dodge", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Company Size",
       subtitle = "Number of employees",
       x = "Company Size",
       y = "Count")

ggplot(pt_info, aes(x = factor(experience,
                               levels = c("Less than 1 year",
                                          "1-2 years",
                                          "3-5 years",
                                          "5-10 years",
                                          "10+ years"))))+
  geom_bar(stat = "count", aes(fill = Condition), position = "dodge", alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Work Experience",
       subtitle = "",
       x = "Years of Experience",
       y = "Count")


ggplot(pt_info, aes(x = risk))+
  geom_bar(stat = "count", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Risk Aversion",
       x = "Average Response to Risk Items",
       y = "Count")+
  facet_grid(Condition ~.)+
  theme(strip.text.y = element_text(angle = 0))

```



## Summary Stats

Here, we examine some basic information about how ratings for different applicants varied. 

```{r summary stats}

average_ratings <- analysis %>% 
  group_by(Condition) %>% 
  summarise(avg_rating = mean(rating),
            standard_dev = sd(rating),
            max = avg_rating+ standard_dev,
            min = avg_rating - standard_dev,
            n = n())
average_ratings

gender_ratings <- analysis %>% 
  group_by(applicant_gender) %>% 
  summarise(avg_rating = mean(rating),
            standard_dev = sd(rating))
gender_ratings

education_ratings <- analysis %>% 
  group_by(applicant_education) %>% 
  summarise(avg_rating = mean(rating),
            standard_dev = sd(rating))
education_ratings

ggplot(analysis, aes(x = rating))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$rating), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$rating), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$rating), color = w_nt, linewidth = 1.25)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$rating), color = m_nt)+
  geom_vline(xintercept = 5, color = lightgray)+
  labs(title = "Distribution of Participant Ratings by Condition",
       #       subtitle = "Vertical lines indicates average rating",
       x = "Rating",
       y = "Count")

ggplot(analysis, aes(x = rating))+
  geom_bar(stat = "count", aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  facet_grid(Condition ~ .)+
  labs(title = "Rating Distributions by Condition",
       x = "Rating",
       y = "Count")+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = "none")

#m_t
ggplot(subset(analysis, Condition == 'Man_Traditional'), aes(x = rating))+
  geom_bar(fill = m_t)+
  labs(title = "Distributions of Resume Ratings: Man, Traditional",
       x = "Rating",
       y = "Count")+
  geom_vline(xintercept = mean(subset(analysis, Condition == 'Man_Traditional')$rating), color = darkgray)+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = "none")

#w_t
ggplot(subset(analysis, Condition == 'Woman_Traditional'), aes(x = rating))+
  geom_bar(fill = w_t)+
  labs(title = "Distributions of Resume Ratings: Woman, Traditional",
       x = "Rating",
       y = "Count")+
  geom_vline(xintercept = mean(subset(analysis, Condition == 'Woman_Traditional')$rating), color = darkgray)+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = "none")

#m_nt
ggplot(subset(analysis, Condition == 'Man_Traditional'), aes(x = rating))+
  geom_bar(fill = m_nt)+
  labs(title = "Distributions of Resume Ratings: Man, Non-Traditional",
       x = "Rating",
       y = "Count")+
  geom_vline(xintercept = mean(subset(analysis, Condition == 'Man_Traditional')$rating), color = darkgray)+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = "none")

#w_nt
ggplot(subset(analysis, Condition == 'Woman_Traditional'), aes(x = rating))+
  geom_bar(fill = w_nt)+
  labs(title = "Distributions of Resume Ratings: Woman, Non-Traditional",
       x = "Rating",
       y = "Count")+
  geom_vline(xintercept = mean(subset(analysis, Condition == 'Woman_Traditional')$rating), color = darkgray)+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = "none")

ggplot(analysis, aes(y = rating, x = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  theme(legend.position = "none")+
  labs(title = "Distribution of Ratings by Condition",
       y = "Rating")

```

```{r scale_summaries}

## technical scale
analysis %>%
  group_by(Condition) %>% 
  summarise(mean_technical= mean(technical_scale))
ggplot(analysis, aes(x = technical_scale))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$technical_scale), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$technical_scale), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$technical_scale), color = w_nt)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$technical_scale), color = m_nt)+
  labs(title = "Distribution of Technical Scale Ratings by Condition",
       subtitle = "Vertical lines indicate group means",
       x = "Rating",
       y = "Count")+
  theme(legend.position = "none")

## leadership scale
analysis %>%
  group_by(Condition) %>% 
  summarise(mean_leadership= mean(leadership_scale))
ggplot(analysis, aes(x = leadership_scale))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$leadership_scale), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$leadership_scale), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$leadership_scale), color = w_nt)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$leadership_scale), color = m_nt)+
  labs(title = "Distribution of Leadership Scale Ratings by Condition",
       subtitle = "Vertical lines indicate group means",
       x = "Rating",
       y = "Count")+
  theme(legend.position = "none")


## likeable scale
analysis %>%
  group_by(Condition) %>% 
  summarise(mean_likeable = mean(likeable_scale))
ggplot(analysis, aes(x = likeable_scale))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$likeable_scale), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$likeable_scale), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$likeable_scale), color = w_nt)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$likeable_scale), color = m_nt)+
  labs(title = "Distribution of Likeable Scale Ratings by Condition",
       subtitle = "Vertical lines indicate group means",
       x = "Rating",
       y = "Count")+
  theme(legend.position = "none")

## learner scale
analysis %>%
  group_by(Condition) %>% 
  summarise(mean_learner = mean(learner_scale))
ggplot(analysis, aes(x = learner_scale))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$learner_scale), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$learner_scale), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$learner_scale), color = w_nt)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$learner_scale), color = m_nt)+
  labs(title = "Distribution of Learner Scale Ratings by Condition",
       subtitle = "Vertical lines indicate group means",
       x = "Rating",
       y = "Count")+
  theme(legend.position = "none")

## education scale
analysis %>%
  group_by(Condition) %>% 
  summarise(mean_education = mean(education_scale))
ggplot(analysis, aes(x = education_scale))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$education_scale), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$education_scale), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$education_scale), color = w_nt)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$education_scale), color = m_nt)+
  labs(title = "Distribution of Education Scale Ratings by Condition",
       subtitle = "Vertical lines indicate group means",
       x = "Rating",
       y = "Count")+
  theme(legend.position = "none")

## experience scale
analysis %>%
  group_by(Condition) %>% 
  summarise(mean_experience= mean(experience_scale))
ggplot(analysis, aes(x = experience_scale))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$experience_scale), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$experience_scale), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$experience_scale), color = w_nt)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$experience_scale), color = m_nt)+
  labs(title = "Distribution of Experience Scale Ratings by Condition",
       subtitle = "Vertical lines indicate group means",
       x = "Rating",
       y = "Count")+
  theme(legend.position = "none")

```

## Testing

```{r data table}

d <- data.table(analysis)

```


### No Covariates - Baseline Model

```{r testing without covariates}

## anova testing
summary(d[, aov(rating ~ Condition)])

## follow-up t-tests, holm correction
d[, pairwise.t.test(rating, Condition, p.adjust.method = "bonferroni")]

## linear model
m0 <- d[, lm(rating ~ Condition)]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m0)
bptest(m0)

m0$vcovHC_ <- vcovHC(m0)
coefs_conditions <- coeftest(m0, vcov. = m0$vcovHC_)
coefs_conditions
ci_conditions <- coefci(m0, vcov. = m0$vcovHC_)
ci_conditions

```

Based on the previous tests, we can detect that there *are* significant differences between conditions. This result is shown in the `ANOVA` test, for which post hoc testing indicates differences between the `Woman_Traditional` condition and the conditions `Man_Nontraditional` and `Woman_Nontraditional`. We follow this testing with linear models to more clearly capture the quantitative differences between ratings. 

Specifically, the baseline candidate received a rating, on average of `r round(coefs_conditions[1], 2)` (`r round(ci_conditions, 2)[1,]`). In comparison, men with a nontraditional education were rated lower, by an average of `r round(coefs_conditions[2], 2)` (`r round(ci_conditions, 2)[2,]`). Women with a nontraditional education were also reated lower than men with a traditional education, by an average of `r round(coefs_conditions[3], 2)` (`r round(ci_conditions, 2)[3,]`). Finally, women with a traditional education were actually rated *higher* than men with a traditional education, by an average of `r round(coefs_conditions[4], 2)` (`r round(ci_conditions, 2)[4,]`).

### Applicant Attributes

The previous analysis focused specifically on the conditions shown. we are also interested in the qualities of these conditions, such as the `applicant_gender` & `applicant_education` variables. This will give us a clearer statistical understanding of the input of each quality of the applicant. At this point forward, we use linear models, rather than ANOVA and t-testing. This is to make the content more consistent with the techniques learned in the course.

```{r attributes}

m1 <- d[gender == "Man" | gender == "Woman", lm(rating ~ applicant_gender * applicant_education)]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m1)
bptest(m1)

m1$vcovHC_ <- vcovHC(m1)
coefs_applicants <- coeftest(m1, vcov. = m1$vcovHC_)
coefs_applicants
ci_applicants <- coefci(m1, vcov. = m1$vcovHC_)
ci_applicants

```
In this case, we observe a significant effect of gender overall, but in the opposite direction which we expected. Women, on average, receive a higher rating than men (`r coefs_applicants[2,1]` higher, p = `r coefs_applicants[2, 4]`). We also see a slight effect of education (p = `r coefs_applicants[3,4]`). Specifically, the applicants with a nontraditional education background are rated `r coefs_applicants[3,1]` lower than those with traditional educations. There is no interaction effect observed (p = `r coefs_applicants[4, 4]`).

### Add Risk Aversion

```{r adding risk aversion}

m2 <- d[gender == "Man" | gender == "Woman", lm(rating ~ applicant_gender * applicant_education + risk)]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m2)
bptest(m2)

m2$vcovHC_ <- vcovHC(m2)
coefs_risk <- coeftest(m2, vcov. = m2$vcovHC_)
coefs_risk
ci_risk <- coefci(m2, vcov. = m2$vcovHC_)
ci_risk

```
We add risk aversion scores to the model to capture individual differences in regards to the amount of risk one may be confortable taking on. It does not change the estimations from the previous model.

### Add Participant Gender

```{r adding participant gender}

m3 <- d[, lm(rating ~ applicant_gender * applicant_education + risk + applicant_gender * factor(gender, levels = c("Man", "Woman")))]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m3)
bptest(m3)

m3$vcovHC_ <- vcovHC(m3)
coefs_gender <- coeftest(m3, vcov. = m3$vcovHC_)
coefs_gender
ci_gender <- coefci(m3, vcov. = m3$vcovHC_)
ci_gender

```


### Add Company Size

```{r adding company size}

m4 <- d[, lm(rating ~ applicant_gender * applicant_education + risk + 
               applicant_gender * factor(gender, levels = c("Man", "Woman"))+
               factor(company_size))]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m4)
bptest(m4)

m4$vcovHC_ <- vcovHC(m4)
coefs_company <- coeftest(m4, vcov. = m4$vcovHC_)
coefs_company
ci_company <- coefci(m4, vcov. = m4$vcovHC_)
ci_company

```


### Add Scale Measures

```{r adding scale measures}

m5 <- d[, lm(rating ~ applicant_gender * applicant_education + risk + 
               applicant_gender * factor(gender, levels = c("Man", "Woman"))+
               factor(company_size) +
               technical_scale +
               leadership_scale +
               likeable_scale +
               learner_scale +
               education_scale +
               experience_scale)]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m5)
bptest(m5)

m5$vcovHC_ <- vcovHC(m5)
coefs_measures <- coeftest(m5, vcov. = m5$vcovHC_)
coefs_measures
ci_measures <- coefci(m5, vcov. = m5$vcovHC_)
ci_measures

```

### Model Comparison

```{r anova}

anova(m1, m2, m3, m4, m5)

```


```{r stargazer}

stargazer(
  m1, 
  m2,
  m3,
  m4,
  m5,
  type = 'html',
  se = list(sqrt(diag(m1$vcovHC_)),
            sqrt(diag(m2$vcovHC_)),
            sqrt(diag(m3$vcovHC_)),
            sqrt(diag(m4$vcovHC_)),
            sqrt(diag(m5$vcovHC_))
  ),
 # header=FALSE,
  single.row = TRUE, 
  no.space = TRUE 
)

```

## Follow-up Visualizations

```{r scale_comparisons}

ggplot(subset(analysis, gender == "Man" | gender == "Woman"), aes(y = technical_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Technical Ratings between Conditions",
       subtitle = "Grouped by Education & Participant Gender",
       y = "Technical Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")+
  facet_grid(~ gender)

ggplot(subset(analysis, gender == "Man" | gender == "Woman"), aes(y = education_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Relevant Education Ratings between Conditions",
       subtitle = "Grouped by Education & Participant Gender",
       y = "Education Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")+
  facet_grid(~ gender)

ggplot(subset(analysis, gender == "Man" | gender == "Woman"), aes(y = experience_scale, x = applicant_gender))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Man", "Woman"))+
  labs(title = "Comparison of Relevant Experience Ratings between Conditions",
       subtitle = "Grouped by Gender & Participant Gender",
       y = "Experience Scale Rating\n",
       x = "\nApplicant Gender")+
  theme(legend.position = "none")+
  facet_grid(~ gender)

ggplot(subset(analysis, gender == "Man" | gender == "Woman"), aes(y = rating, x = applicant_gender))+
  geom_jitter(aes(color = gender), alpha = 0.8)+
  scale_color_manual(values = c(m_t, w_t))+
  geom_boxplot(alpha = 0.8, aes(fill = gender))+
  scale_fill_manual(values = c(m_t, w_t))+
  facet_grid(.~ gender)


```

