---
title: "INFO 241"
author: "CS"
date: "2022-11-09"
output: html_document
---

```{r setup, echo = FALSE}

library(sandwich)
library(lmtest)
library(broom)
library(data.table)
library(tidyverse)
library(stargazer)
library(gridExtra)

# set theme for ggplot
theme_set(theme_minimal())

# set up color scheme
m_nt <- "#C97137"
m_t <- "#E0B190"
w_nt <- "#3F6BA5"
w_t <- "#97B3D8"
color_scheme <- c(m_t, m_nt, w_t, w_nt)
```


```{r load and clean data, echo = FALSE}

df <- read.csv("info241_raw.csv")
df <- cbind(pt = 1:nrow(df), df)

# update the scale column names
cols_old <- colnames(df)
cols_new <- str_replace_all(cols_old, 
                            c(
                              "m_nt" = "man_nontrad",
                              "m_t" = "man_trad", 
                              "w_nt" = "woman_nontrad",
                              "w_t" = "woman_trad",
                              "scale_12" = "scale_education",
                              "scale_13" = "scale_experience",
                              "scale_1" = "scale_technical",
                              "scale_3" = "scale_leadership",
                              "scale_4" = "scale_likeable",
                              "scale_5" = "scale_learner")
)
colnames(df) <- cols_new

df$risk <- rowMeans(df %>% select(contains("risk")))


# make list of columns for participant information
participant_columns <- c('pt', 'age', 'gender', 'gender_5_TEXT', 'employment', 'role', 'company_size', 'experience', 'roles', 'industry', 'industry_12_TEXT', "risk", "Condition")
participant_columns_remove <- c('gender_5_TEXT', 'employment', 'role', 'roles', 'industry', 'industry_12_TEXT')

# make participant information df
pt_info <- select(df, all_of(participant_columns))

# make analysis df
analysis <- df %>%
  select(matches(c("man")))
analysis <- cbind(pt = df$pt, analysis)

# use gather to make long data from wide data
analysis <- gather(df, source, rating, colnames(analysis %>% select(matches("man")) %>% select(-contains("scale"))))

# split out the source columns
analysis[c("applicant_gender", "applicant_education", "stimuli_number")] <- str_split_fixed(analysis$source, '_', 3)

# remove rows with NA values
analysis <- analysis %>% drop_na(rating) %>% 
  select(-contains("aversion")) %>% 
  select(-all_of(participant_columns_remove))

# condense across scale ratings
# create lists of columns to condense
technical_scale_cols <- colnames(analysis %>% select(matches("scale_technical")))
leadership_scale_cols <- colnames(analysis %>% select(matches("scale_leadership")))
likeable_scale_cols <- colnames(analysis %>% select(matches("scale_likeable")))
learner_scale_cols <- colnames(analysis %>% select(matches("scale_learner")))
education_scale_cols <- colnames(analysis %>% select(matches("scale_education")))
experience_scale_cols <- colnames(analysis %>% select(matches("scale_experience")))
# condense and remove columns
analysis <- analysis %>%
  mutate(technical_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[technical_scale_cols], sep = ",")), "NA,"), ",NA"),
         leadership_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[leadership_scale_cols], sep = ",")), "NA,"), ",NA"),
         likeable_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[likeable_scale_cols], sep = ",")), "NA,"), ",NA"),
         learner_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[learner_scale_cols], sep = ",")), "NA,"), ",NA"),
         education_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[education_scale_cols], sep = ",")), "NA,"), ",NA"),
         experience_scale = str_remove_all(str_remove_all(do.call(paste, c(analysis[experience_scale_cols], sep = ",")), "NA,"), ",NA")) %>% 
  select(technical_scale, leadership_scale, likeable_scale, learner_scale, education_scale, experience_scale, 
         colnames(analysis)[! colnames(analysis) %in% c(technical_scale_cols, leadership_scale_cols,
                                                        likeable_scale_cols, learner_scale_cols, education_scale_cols,
                                                        experience_scale_cols, "stimuli_number", "source", "Iteration")])

# move into separate rows and remove duplicates
analysis <- analysis %>% 
  mutate(technical_scale = strsplit(technical_scale, ","),
         leadership_scale = strsplit(leadership_scale, ","),
         likeable_scale = strsplit(likeable_scale, ","),
         learner_scale = strsplit(learner_scale, ","),
         education_scale = strsplit(education_scale, ","),
         experience_scale = strsplit(experience_scale, ",")
  ) %>% 
  unnest(c(technical_scale,
           leadership_scale,
           likeable_scale,
           learner_scale,
           education_scale,
           experience_scale)
  )%>% 
  distinct()

# make scales numeric
analysis <- analysis %>% 
  mutate(technical_scale = as.numeric(unlist(technical_scale)),
         leadership_scale = as.numeric(unlist(leadership_scale)),
         likeable_scale = as.numeric(unlist(likeable_scale)),
         learner_scale = as.numeric(unlist(learner_scale)),
         education_scale = as.numeric(unlist(education_scale)),
         experience_scale = as.numeric(unlist(experience_scale))
  )

# create reference condition for analyses
analysis$Condition <- factor(analysis$Condition, levels = c("Man_Traditional", "Man_Nontraditional", "Woman_Traditional", "Woman_Nontraditional"))
analysis$applicant_gender <- relevel(factor(analysis$applicant_gender), ref = "man")
analysis$applicant_education <- relevel(factor(analysis$applicant_education), ref = "trad")

```

## Participant Information 

Here, we examine participant demographics, such as their age and gender, in addition to information about their work industry and experience. Overall, our sample is highly skewed in terms of gender. A representative average participant would be a man who works in a relatively large technology company with some years of experience. 

```{r descriptive_information, echo = FALSE}

lightgray <- "#c5c5c5"
darkgray <- "#555555"

age_dist <- ggplot(pt_info, aes(x = age))+
  geom_histogram(fill = lightgray)+
  geom_vline(aes(xintercept = mean(age)), color = darkgray)+
  labs(title = "Distribution of Participant Age",
       subtitle = paste0("Average age is about ", round(mean(pt_info$age), 0)),
       x = "Age",
       y = "Count")
age_dist

gender_dist <- ggplot(pt_info, aes(x = as.factor(gender)))+
  geom_bar(stat = "count", position= "dodge", fill = lightgray)+
  scale_x_discrete(limits = c("Man", "Woman", "Non-binary / third gender", "Prefer not to say"))+
  labs(title = "Distribution of Participant Gender",
       subtitle = paste0("Sample was about ", 
                         round(nrow(subset(pt_info, gender == "Man"))/nrow(pt_info), 2) * 100,
                         "% Men"),
       x = "Reported Gender",
       y = "Count")
gender_dist

employment_dist <- ggplot(pt_info, aes(x = as.factor(employment)))+
  geom_bar(stat = "count", position= "dodge", fill = lightgray)+
  labs(title = "Distribution of Participant Employment Status", 
       subtitle = paste0(
         round(
           nrow(subset(pt_info, employment == "Employed full time"))/nrow(pt_info), 
           2) * 100,
         "% of respondents were employed full time; this was our aim."),
       x = "Employment Status",
       y = "Count")
employment_dist

industry_df <- pt_info %>% 
  mutate(across('industry', str_replace_all, c('Transportation, utilities, or wholesale' = 'Transportation utilities or wholesale',
                                               "Agriculture, mining, or construction" = "Agriculture mining or construction"))) %>% 
  unnest(industry) %>% 
  mutate(industry = strsplit(industry, ",")) %>%
  unnest(industry )%>% 
  group_by(industry) %>% 
  summarise(ct = n()) %>% 
  arrange(desc(ct)) 
industry_dist <- ggplot(industry_df %>% top_n(10) , aes(x = factor(industry, levels = industry), y  = ct))+
  geom_bar(stat = "identity", fill = lightgray)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Distribution of Participant Industry", 
       subtitle = paste0(
         round(subset(industry_df, industry == "Technology")$ct / nrow(pt_info), 2) * 100,
         "% of participants work in Tehcnology"
       ),
       x = "Industry Area",
       y = "Count")
industry_dist


size_dist <- ggplot(pt_info, aes(x = factor(str_replace_all(company_size, " employees", ""),
                                            levels = c("Less than 50",
                                                       "50-100",
                                                       "100-500",
                                                       "500-1,000",
                                                       "1,000+"))))+
  geom_bar(stat = "count", fill = lightgray)+
  labs(title = "Distribution of Participant Company Size",
       subtitle = "Number of employees",
       x = "Company Size",
       y = "Count")
size_dist

experience_dist <- ggplot(pt_info, aes(x = factor(experience,
                                                  levels = c("Less than 1 year",
                                                             "1-2 years",
                                                             "3-5 years",
                                                             "5-10 years",
                                                             "10+ years"))))+
  geom_bar(stat = "count", fill = lightgray)+
  labs(title = "Distribution of Participant Work Experience",
       subtitle = "",
       x = "Years of Experience",
       y = "Count")
experience_dist

risk_dist <- ggplot(pt_info, aes(x = risk))+
  geom_bar(stat = "count", fill = lightgray)+
  geom_vline(aes(xintercept = mean(risk)), color = darkgray)+
  labs(title = "Distribution of Participant Risk Aversion",
       subtitle = paste0("Average risk score is about ", round(mean(pt_info$risk), 2)),
       x = "Average Response to Risk Items",
       y = "Count")
risk_dist

```

### Covariate checks between conditions

```{r covariate_checks}

ggplot(pt_info, aes(x = age))+
  geom_histogram(bins = 30, aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Age",
       subtitle = "Age was relatively similar across conditions.",
       x = "Age",
       y = "Count")+
  facet_grid(Condition ~ .)+
  theme(strip.text.y = element_text(angle = 0))

pt_info %>% 
  group_by(Condition) %>% 
  summarise(avg_age = mean(age))

ggplot(pt_info, aes(x = as.factor(gender)))+
  geom_bar(stat = "count", position= "dodge", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  scale_x_discrete(limits = c("Man", "Woman", "Non-binary / third gender", "Prefer not to say"))+
  labs(title = "Distribution of Participant Gender and Condition",
       subtitle = "Gender was relatively similar across conditions.",
       x = "Reported Gender",
       y = "Count")

industry_dist <- ggplot(industry_df %>% top_n(10) , aes(x = factor(industry, levels = industry), y  = ct))+
  geom_bar(stat = "identity", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Distribution of Participant Industry", 
       subtitle = paste0(
         round(subset(industry_df, industry == "Technology")$ct / nrow(pt_info), 2) * 100,
         "% of participants work in Tehcnology"
       ),
       x = "Industry Area",
       y = "Count")


ggplot(pt_info, aes(x = factor(str_replace_all(company_size, " employees", ""),
                               levels = c("Less than 50",
                                          "50-100",
                                          "100-500",
                                          "500-1,000",
                                          "1,000+"))))+
  geom_bar(stat = "count", position = "dodge", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Company Size",
       subtitle = "Number of employees",
       x = "Company Size",
       y = "Count")
chisq.test(pt_info$company_size, pt_info$Condition)


ggplot(pt_info, aes(x = factor(experience,
                               levels = c("Less than 1 year",
                                          "1-2 years",
                                          "3-5 years",
                                          "5-10 years",
                                          "10+ years"))))+
  geom_bar(stat = "count", aes(fill = Condition), position = "dodge", alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Work Experience",
       subtitle = "",
       x = "Years of Experience",
       y = "Count")
chisq.test(pt_info$experience, pt_info$Condition)


ggplot(pt_info, aes(x = risk))+
  geom_bar(stat = "count", aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  labs(title = "Distribution of Participant Risk Aversion",
       x = "Average Response to Risk Items",
       y = "Count")+
  facet_grid(Condition ~.)+
  theme(strip.text.y = element_text(angle = 0))

```

```{r randomization check}

pt_info_dt <- data.table(pt_info)

# check for gender treatment
pt_info_dt[, applicant_gender_bin := ifelse(Condition == "Man_Traditional" | Condition == "Man_Nontraditional", 
                                            0, 1)]
null_gender_mod <- pt_info_dt[, lm(applicant_gender_bin ~ 1)]
full_gender_mod <- pt_info_dt[ , lm(applicant_gender_bin ~ 1 + 
                                      age + 
                                      gender + 
                                      company_size + 
                                      factor(experience,
                                             levels = c("Less than 1 year",
                                                        "1-2 years",
                                                        "3-5 years",
                                                        "5-10 years",
                                                        "10+ years"))+
                                      factor(str_replace_all(company_size, " employees", ""),
                                             levels = c("Less than 50",
                                                        "50-100",
                                                        "100-500",
                                                        "500-1,000",
                                                        "1,000+"))
)]
anova(null_gender_mod, full_gender_mod)

# check for education treatment
pt_info_dt[, applicant_education_bin := ifelse(Condition == "Man_Traditional" | Condition == "Woman_Traditional", 
                                            0, 1)]
null_education_mod <- pt_info_dt[, lm(applicant_education_bin ~ 1)]
full_education_mod <- pt_info_dt[, lm(applicant_education_bin ~ 1 + 
                                      age + 
                                      gender + 
                                      company_size + 
                                      factor(experience,
                                             levels = c("Less than 1 year",
                                                        "1-2 years",
                                                        "3-5 years",
                                                        "5-10 years",
                                                        "10+ years"))+
                                      factor(str_replace_all(company_size, " employees", ""),
                                             levels = c("Less than 50",
                                                        "50-100",
                                                        "100-500",
                                                        "500-1,000",
                                                        "1,000+"))
)]
anova(null_education_mod, full_education_mod)

# check for interaction treatment
pt_info_dt[, applicant_interaction_bin := ifelse(Condition == "Woman_Nontraditional", 
                                            1, 0)]
null_interaction_mod <- pt_info_dt[, lm(applicant_interaction_bin ~ 1)]
full_interaction_mod <- pt_info_dt[, lm(applicant_interaction_bin ~ 1 + 
                                      age + 
                                      gender + 
                                      company_size + 
                                      factor(experience,
                                             levels = c("Less than 1 year",
                                                        "1-2 years",
                                                        "3-5 years",
                                                        "5-10 years",
                                                        "10+ years"))+
                                      factor(str_replace_all(company_size, " employees", ""),
                                             levels = c("Less than 50",
                                                        "50-100",
                                                        "100-500",
                                                        "500-1,000",
                                                        "1,000+"))
)]
anova(null_interaction_mod, full_interaction_mod)


```

## Summary Stats

Here, we examine some basic information about how ratings for different applicants varied. 

```{r summary stats}

average_ratings <- analysis %>% 
  group_by(Condition) %>% 
  summarise(avg_rating = mean(rating),
            standard_dev = sd(rating),
            max = avg_rating+ standard_dev,
            min = avg_rating - standard_dev,
            n = n())
average_ratings

gender_ratings <- analysis %>% 
  group_by(applicant_gender) %>% 
  summarise(avg_rating = mean(rating),
            standard_dev = sd(rating))
gender_ratings

education_ratings <- analysis %>% 
  group_by(applicant_education) %>% 
  summarise(avg_rating = mean(rating),
            standard_dev = sd(rating))
education_ratings

ggplot(analysis, aes(x = rating))+
  geom_density(stat = "count",aes(fill = Condition), alpha = 0.8)+
  scale_fill_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$rating), color = w_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$rating), color = m_t)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$rating), color = w_nt, linewidth = 1.25)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$rating), color = m_nt)+
  geom_vline(xintercept = 5, color = lightgray)+
  labs(title = "Distribution of Participant Ratings by Condition",
       #       subtitle = "Vertical lines indicates average rating",
       x = "Rating",
       y = "Count")

ggplot(analysis, aes(x = rating))+
  geom_bar(stat = "count", aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  facet_grid(Condition ~ .)+
  labs(title = "Rating Distributions by Condition",
       x = "Rating",
       y = "Count")+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = "none")

ggplot(analysis, aes(x = rating, y = Condition))+
  scale_y_discrete(limits = c("Man_Traditional", "Man_Nontraditional", "Woman_Traditional", "Woman_Nontraditional"))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$rating), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$rating), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$rating), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$rating), color = m_nt, linewidth = 1.5, alpha = 0.5)+
  geom_hline(yintercept = 5, color = lightgray, linewidth = 1.25)+
  theme(legend.position = "none")+
  labs(title = "Distribution of Ratings by Condition",
       x = "Rating")

```

```{r scale_summaries}

## technical scale
ggplot(analysis, aes(x = technical_scale, y = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$technical_scale), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$technical_scale), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$technical_scale), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$technical_scale), color = m_nt, linewidth = 1.5)+
  labs(title = "Technical Scale Ratings",
       x = "Rating",
       y = "Condition")+
  theme(legend.position = "none", plot.title = element_text(size=22), axis.text.y=element_blank())

## leadership scale
ggplot(analysis, aes(x = leadership_scale, y = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$leadership_scale), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$leadership_scale), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$leadership_scale), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$leadership_scale), color = m_nt, linewidth = 1.5)+
  labs(title = "Leadership Scale Ratings",
       x = "Rating",
       y = "Condition")+
  theme(legend.position = "none", plot.title = element_text(size=22), axis.text.y=element_blank())

## likeable scale
ggplot(analysis, aes(x = likeable_scale, y = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$likeable_scale), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$likeable_scale), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$likeable_scale), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$likeable_scale), color = m_nt, linewidth = 1.5)+
  labs(title = "Likeable Scale Ratings",
       x = "Rating",
       y = "Condition")+
  theme(legend.position = "none", plot.title = element_text(size=22), axis.text.y=element_blank())

## learner scale
ggplot(analysis, aes(x = learner_scale, y = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$learner_scale), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$learner_scale), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$learner_scale), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$learner_scale), color = m_nt, linewidth = 1.5)+
  labs(title = "Learner Scale Ratings",
       x = "Rating",
       y = "Condition")+
  theme(legend.position = "none", plot.title = element_text(size=22), axis.text.y=element_blank())

## education scale
ggplot(analysis, aes(x = education_scale, y = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$education_scale), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$education_scale), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$education_scale), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$education_scale), color = m_nt, linewidth = 1.5)+
  labs(title = "Education Scale Ratings",
       x = "Rating",
       y = "Condition")+
  theme(legend.position = "none", plot.title = element_text(size=22), axis.text.y=element_blank())

## experience scale
ggplot(analysis, aes(x = experience_scale, y = Condition))+
  geom_jitter(aes(color = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Traditional")$experience_scale), color = w_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Traditional")$experience_scale), color = m_t, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Woman_Nontraditional")$experience_scale), color = w_nt, linewidth = 1.5)+
  geom_vline(xintercept = mean(subset(analysis, Condition == "Man_Nontraditional")$experience_scale), color = m_nt, linewidth = 1.5)+
  labs(title = "Experience Scale Ratings",
       x = "Rating",
       y = "Condition")+
  theme(legend.position = "none", plot.title = element_text(size=22), axis.text.y=element_blank())


```

## Testing

```{r data table}

d <- data.table(analysis)
d <- d[gender == "Man" | gender == "Woman"]

```

### ANOVA

```{r anova}

## anova testing
summary(d[, aov(rating ~ Condition)])

## follow-up t-tests, holm correction
d[, pairwise.t.test(rating, Condition, p.adjust.method = "bonferroni")]

```

Based on the previous tests, we can detect that there *are* significant differences between conditions. This result is shown in the `ANOVA` test, for which post hoc testing indicates differences between the `Woman_Traditional` condition and the conditions `Man_Nontraditional` and `Woman_Nontraditional`. We follow this testing with linear models to more clearly capture the quantitative differences between ratings. 

### No Covariates - Baseline Model

The previous analysis focused specifically on the conditions shown. We are also interested in the qualities of these conditions, such as the `applicant_gender` & `applicant_education` variables. This will give us a clearer statistical understanding of the input of each quality of the applicant. At this point forward, we use linear models, rather than ANOVA and t-testing. This is to make the content more consistent with the techniques learned in the course.

```{r baseline}

m1 <- d[, lm(rating ~ applicant_gender * applicant_education)]

# test for heteroscedasticity to determine if use of robust standard errors is justified
plot(m1)
bptest(m1)

m1$vcovHC_ <- vcovHC(m1)
coefs_applicants <- coeftest(m1, vcov. = m1$vcovHC_)
coefs_applicants
ci_applicants <- coefci(m1, vcov. = m1$vcovHC_)
ci_applicants

```
In this case, we observe a significant effect of gender overall, but in the opposite direction which we expected. Women, on average, receive a higher rating than men (`r coefs_applicants[2,1]` higher, p = `r coefs_applicants[2, 4]`). We also see a slight effect of education (p = `r coefs_applicants[3,4]`). Specifically, the applicants with a nontraditional education background are rated `r coefs_applicants[3,1]` lower than those with traditional educations. There is no interaction effect observed (p = `r coefs_applicants[4, 4]`).

### Add Risk Aversion

```{r adding risk aversion}

m2 <- d[, lm(rating ~ applicant_gender * applicant_education + risk)]

# test for heteroscedasticity to determine if use of robust standard errors is justified
plot(m2)
bptest(m2)

m2$vcovHC_ <- vcovHC(m2)
coefs_risk <- coeftest(m2, vcov. = m2$vcovHC_)
coefs_risk
ci_risk <- coefci(m2, vcov. = m2$vcovHC_)
ci_risk

```
We add risk aversion scores to the model to capture individual differences in regards to the amount of risk one may be confortable taking on. It does not change the estimations from the previous model.

### Add Participant Gender

```{r adding participant gender}

m3 <- d[, lm(rating ~ applicant_gender * applicant_education + risk + applicant_gender * factor(gender))]

# test for heteroscedasticity to determine if use of robust standard errors is justified
par(mfrow = c(2, 2))
plot(m3)
bptest(m3)

m3$vcovHC_ <- vcovHC(m3)
coefs_gender <- coeftest(m3, vcov. = m3$vcovHC_)
coefs_gender
ci_gender <- coefci(m3, vcov. = m3$vcovHC_)
ci_gender

```


### Add Company Size

```{r adding company size}

m4 <- d[, lm(rating ~ applicant_gender * applicant_education + risk + 
               applicant_gender * factor(gender)+
               factor(company_size))]

# test for heteroscedasticity to determine if use of robust standard errors is justified
plot(m4)
bptest(m4)

m4$vcovHC_ <- vcovHC(m4)
coefs_company <- coeftest(m4, vcov. = m4$vcovHC_)
coefs_company
ci_company <- coefci(m4, vcov. = m4$vcovHC_)
ci_company

```

### Add Years of Experience

```{r adding experience}


m5 <- d[, lm(rating ~ applicant_gender * applicant_education + risk + 
               applicant_gender * factor(gender)+
               factor(company_size) +
               factor(experience))]

# test for heteroscedasticity to determine if use of robust standard errors is justified
plot(m5)
bptest(m5)

m5$vcovHC_ <- vcovHC(m5)
coefs_experience <- coeftest(m5, vcov. = m5$vcovHC_)
coefs_experience
ci_experience <- coefci(m5, vcov. = m5$vcovHC_)
ci_experience

```

Now that we have included all covariates, we can interpret this model & examine the role of applicant gender and education, as well as the role of the various covariates.

### Model Comparison

```{r model_anova}

anova(m1, m2, m3, m4, m5)

```


```{r stargazer}

stargazer(
  m1, 
  m2,
  m3,
  m4,
  m5,
  type = 'html',
  se = list(sqrt(diag(m1$vcovHC_)),
            sqrt(diag(m2$vcovHC_)),
            sqrt(diag(m3$vcovHC_)),
            sqrt(diag(m4$vcovHC_)),
            sqrt(diag(m5$vcovHC_))
  ),
 # header=FALSE,
  single.row = TRUE, 
  no.space = TRUE 
)

```

### Predict Scale Measures

We also collected scale responses to indicate further which aspects of an applicant may be supporting the rating provided. Here, we conduct **exploratory** analysis to examine how the factors of an application may also influence the ratings of these scales. In this case, we do not examine covariates. This is to limit the amount of significance testing performed in these exploratory models. We do not state any causal claims, but rather use these models to indicate possible explanations for differences in overall ratings between different genders and education backgrounds.

```{r technical_scale}

m_technical <- d[, lm(technical_scale ~ applicant_gender * applicant_education)]

m_technical$vcovHC_ <- vcovHC(m_technical)
coefs_technical <- coeftest(m_technical, vcov. = m_technical$vcovHC_)
coefs_technical

ggplot(analysis, aes(y = technical_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Technical Ratings between Conditions",
       y = "Technical Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")

```


```{r leadership_scale}

m_leadership <- d[, lm(leadership_scale ~ applicant_gender * applicant_education)]

m_leadership$vcovHC_ <- vcovHC(m_leadership)
coefs_leadership <- coeftest(m_leadership, vcov. = m_leadership$vcovHC_)
coefs_leadership

ggplot(analysis, aes(y = leadership_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Leadership Ratings between Conditions",
       y = "Leadership Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")

```


```{r likeable_scale}

m_likeable <- d[, lm(likeable_scale ~ applicant_gender * applicant_education)]

m_likeable$vcovHC_ <- vcovHC(m_likeable)
coefs_likeable <- coeftest(m_likeable, vcov. = m_likeable$vcovHC_)
coefs_likeable

ggplot(analysis, aes(y = likeable_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Likeability Ratings between Conditions",
       y = "Likeability Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")

```


```{r learner_scale}

m_learner <- d[, lm(learner_scale ~ applicant_gender * applicant_education)]

m_learner$vcovHC_ <- vcovHC(m_learner)
coefs_learner <- coeftest(m_learner, vcov. = m_learner$vcovHC_)
coefs_learner

ggplot(analysis, aes(y = learner_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Quick Learner Ratings between Conditions",
       y = "Quick Learner Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")

```


```{r education_scale}

m_education <- d[, lm(education_scale ~ applicant_gender * applicant_education)]

m_education$vcovHC_ <- vcovHC(m_education)
coefs_education <- coeftest(m_education, vcov. = m_education$vcovHC_)
coefs_education

ggplot(analysis, aes(y = education_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Relevant Education Ratings between Conditions",
       y = "Relevant Education Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")

```


```{r experience_scale}

m_experience <- d[, lm(experience_scale ~ applicant_gender * applicant_education)]

m_experience$vcovHC_ <- vcovHC(m_experience)
coefs_experience <- coeftest(m_experience, vcov. = m_experience$vcovHC_)
coefs_experience

ggplot(analysis, aes(y = experience_scale, x = applicant_education))+
  geom_jitter(aes(color = Condition), alpha = 0.5)+
  geom_boxplot(alpha = 0.8, aes(fill = Condition))+
  scale_fill_manual(values = color_scheme)+
  scale_color_manual(values = color_scheme)+
  scale_x_discrete(labels = c("Traditional", "Non-Traditional"))+
  labs(title = "Comparison of Relevant Experience Ratings between Conditions",
       y = "Relevant Experience Scale Rating\n",
       x = "\nApplicant Education")+
  theme(legend.position = "none")

```


```{r stargazer_scales}

stargazer(
  m_technical, 
  m_leadership,
  m_likeable,
  m_learner,
  m_education,
  m_experience,
  type = 'html',
  se = list(sqrt(diag(m_technical$vcovHC_)),
            sqrt(diag(m_leadership$vcovHC_)),
            sqrt(diag(m_likeable$vcovHC_)),
            sqrt(diag(m_learner$vcovHC_)),
            sqrt(diag(m_education$vcovHC_)),
            sqrt(diag(m_experience$vcovHC_))
  ),
 # header=FALSE,
  single.row = TRUE, 
  no.space = TRUE 
)

```

## Other Visualizations

```{r participant gender}

ggplot(subset(analysis, gender == "Man" | gender == "Woman"), aes(y = rating, x = applicant_gender))+
  geom_jitter(aes(color = gender), alpha = 0.8)+
  scale_color_manual(values = c(m_t, w_t))+
  geom_boxplot(alpha = 0.8, aes(fill = gender))+
  scale_fill_manual(values = c(m_t, w_t))+
  facet_grid(.~ gender)

```

